The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-17 analysis/paper/paper.qmd
Update ngrams code chunk

## TO DO: generalise bigrams and trigrams into an ngrams function

@@

## Show network of bigrams
bigram_graph <- bigram_counts |> 
  filter(n > 20) |> 
  igraph::graph_from_data_frame()

emu_theses_bigrams_top <- emu_theses_bigrams %>%
  group_by(title) %>%
  count(bigram, sort = TRUE) %>%
  slice_max(n, n = 10) %>%        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  ungroup() %>% 
  mutate(bigram = reorder(bigram, n))

@@

emu_theses_bigrams_top %>%
  ggplot(aes(x = bigram, y = n, fill = title)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  labs(y = "Count",
       x = "Unique words",
       title = "Count of unique words found in thesis",
       subtitle = "Stop words were removed from the list") +
  facet_wrap( ~ title, scales = "free", ncol = 2)

# find the most frequently used bigrams
emu_thesis_bigrams_top <- emu_theses_bigrams %>%
  group_by(title) %>% 
  count(bigram, sort = TRUE) %>%
  slice_max(n, n = 10) %>%                   ### change the number of top words to show
  mutate(bigram = reorder(bigram, n)) %>% 
  print()
```

>>>>

## TO DO: generalise bigrams and trigrams into ngrams function

@@

## Show network of bigrams
bigram_graph <- bigram_counts |> 
  filter(n > 100) |> 
  graph_from_data_frame()

bigram_graph

set.seed(2023)

a <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE, arrow = a) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()

## Higgh frequency bigrams ----

emu_theses_bigrams_top <- emu_theses_bigrams %>%
  group_by(title) %>%
  count(bigram, sort = TRUE) %>%
  slice_max(n, n = 20) %>%        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  ungroup() %>% 
  mutate(bigram = reorder(bigram, n))

@@

emu_theses_bigrams_top %>%
  filter(title == unique(title)[1:6]) |> 
  ggplot(aes(x = bigram, y = n, fill = title)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  labs(y = "Count",
       x = "Unique words",
       title = "Count of unique words found in thesis",
       subtitle = "Stop words were removed from the list") +
  facet_wrap( ~ title, scales = "free", ncol = 2) +
  theme(legend.position = "none") 
```
